\section{Outline of lectures}

16 90 minute lectures

\begin{table} 
    \begin{tabular}{ c | c }
     \textbf{Content}   & \textbf{PyCav integration}  \\ 
       Many particle wavefunctions and statistics 
   & Monte Carlo simulation of Laughlin states. \\ 
      Second quantization. Hartree--Fock theory. Jordan--Wigner.  &  \\ 
      Response functions. Structure factor. Sum rules.    &  \\ 
      Bose gas. Gross--Pitaevskii. Bogoliubov theory \& superfluidity.   & GP equation in traps \\ 
      Fermi gas   &  \\ 
      BCS   & Anderson domain wall  \\ 
      Kondo and scaling theory   &  \\ 
      Quantizing a chain. Phonons   &  \\ 
      Orthogonality castastrophe. Caldeira--Leggett.   &  \\ 
      Strong correlations   &  \\ 
      Ising model and QPT   &  Classical Ising simulation \\ 
      Ferromagnets and Antiferromagnets   & Spin waves and solitons \\ 
      Topological defects   & Skyrmions, Hopfions. \\ 
      Berry phase. Topological band structure   & Textures in Brillouin zone \\ 
      Kitaev model   &  \\ 
      Fractional statistics & 
    \end{tabular} 
\end{table}

\begin{enumerate}
\item Many particle wavefunctions and statistics. Examples of the Fermi gas, Calogero--Sutherland model, and Quantum Hall Effect.

\item Second quantization. Hartree--Fock theory.

\item Response functions. Structure factor. Sum rules. 

\item Bose gas. Gross--Pitaevskii. Bogoliubov theory and superfluidity.

\item Fermi gas. Trial wavefunction describing quasiparticles. Quasiparticle residue. Landau theory via perturbation theory. RPA?

\item Cooper divergences. BCS theory and superconductivity. 

\item Kondo divergences and scaling theory.

\item Phonons. Quantizing a chain. Hydrodynamic picture and Luttinger liquid.

\item Orthogonality catastrophe. Caldeira--Leggett environment.

\item Tight binding. Hubbard model and Mott transition. Bose--Hubbard.

\item Transverse Ising as quantum phase transition.

\item Heisenberg ferromagnet. Magnons. Antiferromagnetic order. Symmetry breaking

\item Topological defects. Vortices, Skyrmions. 

\item Berry phase. Magnetic monopoles. Topological Band structure.

\item Kitaev model?

\item Fractional statistics?
\end{enumerate}